analisis-preliminar

### 2021-04-22 production/analisis-preliminar.Rmd
update

data_proc=data %>% dplyr::select(igualdad.est,esp_publico.est,esp_privado.est,Sexo,ap_discusion,mean_discusion,num_fem,RBD,igualdad.pad,esp_publico.pad,esp_privado.pad,Educacion,Libros_apod,Libros_apod_rec,quintiles_ingresos_pc_factor,dependencia,REGION,c_civic) %>% as.data.frame() #,igualdad.pad_c,Educacion_c,igualdad.est_c,mean_ig_pad,mean_educacion,mean_ig_est,esp_publico.pad_c,esp_publico.est_c,mean_pub_pad,mean_pub_est,esp_privado.pad_c,esp_privado.est_c,mean_priv_pad,mean_priv_est,Libros_apod_c,mean_libros_apod

@@

data_proc1=data %>% dplyr::select(igualdad.est,esp_publico.est,esp_privado.est,Sexo,ap_discusion,mean_discusion,num_fem,RBD,igualdad.pad,esp_publico.pad,esp_privado.pad,Educacion,Libros_apod_rec,quintiles_ingresos_pc_factor,igualdad.pad_c,Educacion_c,igualdad.est_c,mean_ig_pad,mean_educacion,mean_ig_est,esp_publico.pad_c,esp_publico.est_c,mean_pub_pad,mean_pub_est,esp_privado.pad_c,esp_privado.est_c,mean_priv_pad,mean_priv_est,Libros_apod_c,mean_libros_apod,dependencia,REGION,c_civic) %>% as.data.frame()

>>>>

data_proc=data %>% 
  dplyr::select(
    igualdad.est,
    esp_publico.est,
    esp_privado.est,
    Sexo,
    ap_discusion,
    mean_discusion,
    num_fem,
    RBD,
    igualdad.pad,
    esp_publico.pad,
    esp_privado.pad,
    Educacion,
    Libros_apod,
    Libros_apod_rec,
    quintiles_ingresos_pc_factor,
    dependencia,
    REGION,
    c_civic
  ) %>% as.data.frame() 

@@

data_proc1=data %>% dplyr::select(
  igualdad.est,
  esp_publico.est,
  esp_privado.est,
  Sexo,
  ap_discusion,
  mean_discusion,
  num_fem,
  RBD,
  igualdad.pad,
  esp_publico.pad,
  esp_privado.pad,
  Educacion,
  Libros_apod_rec,
  quintiles_ingresos_pc_factor,
  igualdad.pad_c,
  Educacion_c,
  igualdad.est_c,
  mean_ig_pad,
  mean_educacion,
  mean_ig_est,
  esp_publico.pad_c,
  esp_publico.est_c,
  mean_pub_pad,
  mean_pub_est,
  esp_privado.pad_c,
  esp_privado.est_c,
  mean_priv_pad,
  mean_priv_est,
  Libros_apod_c,
  mean_libros_apod,
  dependencia,
  REGION,
  c_civic
) %>% as.data.frame()
